Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-11-11 02_paper/02_study/02_expertise_paper/expertise_2024_09_24_outlierdetection_MK.Rmd
x - adding all Aois

>>>>

#### 2.2.3 Number of fixations (AOI others)
```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

##################### NUMBER OF FIXATIONS (AOI others) ########################

# filter group & total duration & number fixation (AOI others)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Board_Screen",
    "Total_duration_of_fixations.Classroom_Others",
    "Total_duration_of_fixations.Material_Students",
    "Total_duration_of_fixations.Material_Teacher",
    "Total_duration_of_fixations.Nametag_Anna",
    "Total_duration_of_fixations.Nametag_Bianca",
    "Total_duration_of_fixations.Nametag_Carl(a)",
    "Number_of_fixations.Board_Screen",
    "Number_of_fixations.Classroom_Others",
    "Number_of_fixations.Material_Students",
    "Number_of_fixations.Material_Teacher",
    "Number_of_fixations.Nametag_Anna",
    "Number_of_fixations.Nametag_Bianca",
    "Number_of_fixations.Nametag_Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
    Participant = Participant,
    Others_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Others_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Others_number_fixation_min = round(Others_number_fixation / Duration_of_interval_min, digits = 2),
    Average_duration_others = round(Others_duration_fixation / Others_number_fixation, digits = 0)
    ) -> df_aoi_others

# filter only for experts
df_aoi_others_expert <- df_aoi_others %>% 
  filter(Group == "Expert")

# filter only for novices
df_aoi_others_novice <- df_aoi_others %>% 
  filter(Group == "Novice")

# Boxplot showing outliers for experts
ggplot(df_aoi_others_expert, aes(x = "", y = Others_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of number of fixations per minute (AOI others)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_others_expert$Others_number_fixation_min, 0.25)
Q3 <- quantile(df_aoi_others_expert$Others_number_fixation_min, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_others_exp <- df_aoi_others_expert %>%
  filter(Others_number_fixation_min >= LowerBound & Others_number_fixation_min <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_others_expert)  # Original data
nrow(df_no_outliers_others_exp)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_others_exp <- df_aoi_others_expert %>%
  filter(Others_number_fixation_min < LowerBound | Others_number_fixation_min > UpperBound)

# View the removed outliers
df_outliers_others_exp

# Boxplot showing outliers for novices
ggplot(df_aoi_others_novice, aes(x = "", y = Others_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of number of fixations per minute (AOI others)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_others_novice$Others_number_fixation_min, 0.25)
Q3 <- quantile(df_aoi_others_novice$Others_number_fixation_min, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_others_nov <- df_aoi_others_novice %>%
  filter(Others_number_fixation_min >= LowerBound & Others_number_fixation_min <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_others_novice)  # Original data
nrow(df_no_outliers_others_nov)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_others_nov <- df_aoi_others_novice %>%
  filter(Others_number_fixation_min < LowerBound | Others_number_fixation_min > UpperBound)

# View the removed outliers
df_outliers_others_nov

### 2024-11-11 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x - adding all Aois

---
title: "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study"
output: 
  pdf_document:
    toc: true           # Add a table of contents
    number_sections: true
    latex_engine: xelatex  # Specify LaTeX engine if needed
    keep_tex: true      # Keep .tex file for debugging or customization
---

@@

## 1. Participants
```{r demographicstable, include = TRUE, echo=FALSE}

@@

## 2. Measures

### 2.1 Eye-Tracking Data
```{r eyetracking_read_in_data, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

@@

#### 2.2.2 Letter search
```{r letter_search, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.1 Number of fixations per minute (micro-teaching unit)
```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.2 Number of fixations per minute (AOI students)
```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.2 Number of fixations per minute (AOI others)
```{r nof_others, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

@@

#### 2.2.3 Number of fixations (AOI disruptive person)
```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.4 Average duration of fixations in milliseconds (micro-teaching unit)
```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.5 Average duration of fixations (AOI students)
```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.6 Average duration of fixations (AOI disruptive person)
```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.7 Gaze Relational Index (GRI; micro-teaching unit)
```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### 2.2.10 Time to first fixation in seconds (AOI disruptive person)
```{r ttff_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### 2.2 Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
```{r rating_scales, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

# ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# ############## Prevalence Rating #########################
# 
# sri.preva.table <-
#   sri %>%
#   group_by(ID) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.table,
#              caption = "Prevalence rating")
# 
# #### with event 
# sri.preva.event.table <-
#   sri %>%
#   group_by(ID, event) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.event.table,
#              caption = "Prevalence rating with events")
# 
# # create a new data frame with rating
# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
# 
# # plotting prevalence rating for groups
# preva_group_plot <- 
#   sri_preva %>% 
#   mutate(ID = factor(ID,
#                      levels = c("Novice",
#                                 "Expert"
#                                 )
#                      )
#          ) %>% 
#   ggplot(mapping = aes(x = ID,
#                        y = prevalence_rating)) +
#   geom_boxplot(mapping = aes(fill = ID),
#                outlier.shape = NA) +
#   geom_point(size = 1,
#              alpha = 0.4,
#              position = position_jitter(seed = 1,
#                                         width = 0.1,
#                                         height = 0.1)) +
#   scale_x_discrete(limits = c("Novice", "Expert")) +
#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
#   labs(x = "",
#        y = "Prevalence Rating") + 
#   scale_fill_brewer(palette  = "RdBu") +  
#   ggtitle("How widespread is this event in the classroom?") +
#   theme_cowplot()
# 
# preva_group_plot
# 
# ```

#### t-Test & effect size "Prevalence rating"
# ```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# #################### T-TEST & EFFECT SIZE ############
# 
# # Prevalence Rating 
# # t-test for expertise differences
# t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
#        y = sri$prevalence_rating[sri$ID == "Novice"],
#        var.equal = TRUE)
# 
# # Prevalence Rating 
# # effect size for expertise differences
# d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
#                       y = sri$prevalence_rating[sri$ID == "Novice"],
#                       na.rm = TRUE)
# 
# round(d_sri_preva, 2)
# 
# ```

@@

### Prevalence Rating as manipulation check
```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# ############## Prevalence Rating as manipulation check #########################
# 
# sri.preva.table <-
#   sri %>%
#   group_by(ID) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.table,
#              caption = "Prevalence rating")
# 
# #### with event 
# sri.preva.event.table <-
#   sri %>%
#   group_by(ID, event) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.event.table,
#              caption = "Prevalence rating with events")
# 
# # create a new data frame with rating
# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
# 
# # plotting prevalence rating for groups
# preva_group_plot <- 
#   sri_preva %>% 
#   mutate(ID = factor(ID,
#                      levels = c("Novice",
#                                 "Expert"
#                                 )
#                      )
#          ) %>% 
#   ggplot(mapping = aes(x = ID,
#                        y = prevalence_rating)) +
#   geom_boxplot(mapping = aes(fill = ID),
#                outlier.shape = NA) +
#   geom_point(size = 1,
#              alpha = 0.4,
#              position = position_jitter(seed = 1,
#                                         width = 0.1,
#                                         height = 0.1)) +
#   scale_x_discrete(limits = c("Novice", "Expert")) +
#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
#   labs(x = "",
#        y = "Prevalence Rating") + 
#   scale_fill_brewer(palette  = "RdBu") +  
#   ggtitle("How widespread is this event in the classroom?") +
#   theme_cowplot()
# 
# preva_group_plot

### 2.3 Situational Jugdement Test
```{r sjt, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### 2.4 Classroom Questionnaire
```{r classroom questionnaire, echo=FALSE, results='asis'}

@@

## 3. Correlations
```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

---
title: "Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study"
output: 
  html_document:
    toc: true           # Add a table of contents
    number_sections: true
---

@@

## Participants
```{r demographicstable, include = TRUE, echo=FALSE}

@@

## Measures

### Eye-Tracking Data
```{r eyetracking_read_in_data, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

@@

#### Letter search
```{r letter_search, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### Fixations per minute across all AOIs
```{r nof_all_aois, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Filter data and select relevant columns, excluding "Disruptive_Person" only for the total fixations
df_aoi_filtered <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Number_of_fixations")
  )

# Add a new AOI 'Students' by summing fixations for Anna, Bianca, and Carl(a)
df_aoi_filtered <- df_aoi_filtered %>%
  mutate(
    Number_of_fixations.Students = 
      `Number_of_fixations.Anna` +
      `Number_of_fixations.Bianca` +
      `Number_of_fixations.Carl(a)`,

    # Calculate Total Fixations for all AOIs, excluding "Disruptive_Person"
    Total_fixations_all = sum(c_across(starts_with("Number_of_fixations"))[!names(c_across(starts_with("Number_of_fixations"))) == "Number_of_fixations.Disruptive_Person"], na.rm = TRUE)
  )

# Convert duration to minutes and calculate fixations per minute
df_aoi_filtered <- df_aoi_filtered %>%
  mutate(Duration_of_interval_min = Duration_of_interval / 60000)

df_aoi_long <- df_aoi_filtered %>%
  rowwise() %>%
  mutate(
    across(starts_with("Number_of_fixations"), ~ .x / Duration_of_interval_min, .names = "fixation_per_min_{.col}")
  ) %>%
  ungroup() %>%
  pivot_longer(
    cols = starts_with("fixation_per_min_Number_of_fixations"),
    names_to = "AOI",
    values_to = "Fixations_per_minute"
  ) %>%
  mutate(AOI = str_remove(AOI, "fixation_per_min_Number_of_fixations.")) %>%
  mutate(AOI = factor(AOI, levels = c("All", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
                                      "Board_Screen", "Material_Teacher", "Material_Students", 
                                      "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"))) %>%
  arrange(AOI)

# Summarize descriptives
aois_descriptives_fixations <- df_aoi_long %>%
  group_by(Group, AOI) %>%
  summarise(
    N = n(),
    M = round(mean(Fixations_per_minute, na.rm = TRUE), 2),
    SD = round(sd(Fixations_per_minute, na.rm = TRUE), 2),
    Min = round(min(Fixations_per_minute, na.rm = TRUE), 2),
    Max = round(max(Fixations_per_minute, na.rm = TRUE), 2)
  )

knitr::kable(nof.table,
             caption = "N, M, SD, min & max number of fixation per minute (across all AOIs)")

# Visualization: Boxplot for fixations per minute across AOIs
ggplot(df_aoi_long, aes(x = AOI, y = Fixations_per_minute, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.15),
    size = 1.5,
    alpha = 0.7
  ) +
  scale_fill_brewer(palette = "RdBu") +
  labs(x = "AOI", y = "Number of fixations per minute") +
  ggtitle("Fixations per minute across all AOIs") +
  theme_minimal() +
  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))

#### Number of fixations per minute (micro-teaching unit)
```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### Number of fixations per minute (AOI students)
```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### Number of fixations per minute (AOI others)
```{r nof_others, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

# plotting number of fixations per minute on AOI Students
df_aoi_others %>%
  ggplot(mapping = aes(x = Group, y = Others_number_fixation_min)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.005
    )
  ) +
  ylim(0, 100) +
  labs(x = "", y = "Number of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per minute\n(AOI others)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_min_others

plot_number_min_others

@@

#### Number of fixations (AOI disruptive person)
```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### Duration of Fixations across all AOIs
```{r average_dur_all_aoi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Filtere und wähle die relevanten Spalten aus
df_aoi_filtered <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations")
  )

# Erstelle die AOI "Students" durch Summieren der Werte für Anna, Bianca und Carl(a)
df_aoi_filtered <- df_aoi_filtered %>%
  mutate(
    Total_duration_of_fixations.Students = 
      `Total_duration_of_fixations.Anna` +
      `Total_duration_of_fixations.Bianca` +
      `Total_duration_of_fixations.Carl(a)`,
    Number_of_fixations.Students = 
      `Number_of_fixations.Anna` +
      `Number_of_fixations.Bianca` +
      `Number_of_fixations.Carl(a)`
  )

# Berechne die durchschnittliche Fixationsdauer für jede AOI individuell (einschließlich "Disruptive_Person")
df_aoi_avg_long <- df_aoi_filtered %>%
  pivot_longer(
    cols = starts_with("Total_duration_of_fixations") | starts_with("Number_of_fixations"),
    names_to = "Measure_AOI",
    values_to = "Values"
  ) %>%
  separate(Measure_AOI, into = c("Measure", "AOI"), sep = "\\.", extra = "merge") %>%
  pivot_wider(
    names_from = Measure,
    values_from = Values
  ) %>%
  mutate(
    Average_duration = round(Total_duration_of_fixations / Number_of_fixations, digits = 2)
  )

# Berechne `Average_duration_mtu` und `Number_fixation_mtu` durch Aufsummieren der Fixationsdauer und -anzahl, ohne "Disruptive_Person"
df_mtu_summary <- df_aoi_filtered %>%
  rowwise() %>%  # Zeilenweise Berechnung
  mutate(
    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations")), na.rm = TRUE) - `Total_duration_of_fixations.Disruptive_Person`,
    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations")), na.rm = TRUE) - `Number_of_fixations.Disruptive_Person`
  ) %>%
  ungroup() %>%
  summarise(
    Group = unique(Group),
    Average_duration_mtu = round(mean(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, na.rm = TRUE), 2),
    Number_fixation_mtu = sum(Total_fixations_excl_disruptive, na.rm = TRUE)
  ) %>%
  mutate(AOI = "MTU")

# Füge `Average_duration_mtu` und `Number_fixation_mtu` zur Langformat-Datenstruktur hinzu
df_aoi_avg_long <- bind_rows(df_aoi_avg_long, df_mtu_summary)

# Setze die AOIs in der gewünschten Reihenfolge, einschließlich "MTU"
df_aoi_avg_long <- df_aoi_avg_long %>%
  mutate(AOI = factor(AOI, levels = c(
    "MTU", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
    "Board_Screen", "Material_Teacher", "Material_Students", 
    "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"
  ))) %>%
  arrange(AOI)

# Berechne deskriptive Statistiken, einschließlich "MTU"
aois_descriptives_durations <- df_aoi_avg_long %>%
  group_by(Group, AOI) %>%
  summarise(
    N = n(),
    M = round(mean(Average_duration, na.rm = TRUE), 2),
    SD = round(sd(Average_duration, na.rm = TRUE), 2),
    Min = round(min(Average_duration, na.rm = TRUE), 2),
    Max = round(max(Average_duration, na.rm = TRUE), 2)
  )

# Visualisierung: Boxplot der durchschnittlichen Fixationsdauer für alle AOIs
ggplot(df_aoi_avg_long, aes(x = AOI, y = Average_duration, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.15),
    size = 1.5,
    alpha = 0.7
  ) +
  scale_fill_brewer(palette = "RdBu") +
  labs(x = "AOI", y = "Average Duration of Fixations (ms)") +
  ggtitle("Average Duration of Fixations across all AOIs") +
  theme_minimal() +
  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))

# Ausgabe der deskriptiven Tabelle, einschließlich "MTU"
knitr::kable(aois_descriptives_durations,
             caption = "N, M, SD, min & max duration of fixations in milliseconds (across all AOIs)")

#### Average duration of fixations in milliseconds (micro-teaching unit)
```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### Average duration of fixations (AOI students)
```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### Average duration of fixations (AOI disruptive person)
```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### Gaze Relational Index (GRI; micro-teaching unit)
```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

#### Time to first fixation in seconds (AOI disruptive person)
```{r ttff_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
```{r rating_scales, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### Prevalence Rating as manipulation check
```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

############## Prevalence Rating #########################

sri.preva.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

knitr::kable(sri.preva.table,
             caption = "Prevalence rating")

sri.preva.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

knitr::kable(sri.preva.event.table,
             caption = "Prevalence rating with events")

sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))

preva_group_plot <- 
  sri_preva %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = prevalence_rating)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Prevalence Rating") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How widespread is this event in the classroom?") +
  theme_cowplot()

preva_group_plot

t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
       y = sri$prevalence_rating[sri$ID == "Novice"],
       var.equal = TRUE)

d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
                      y = sri$prevalence_rating[sri$ID == "Novice"],
                      na.rm = TRUE)

round(d_sri_preva, 2)
```

@@

### Situational Jugdement Test
```{r sjt, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

### Classroom Questionnaire
```{r classroom questionnaire, echo=FALSE, results='asis'}

@@

## Correlations
```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
